[dcpo_demsupport]

### 2020-06-26 paper/dcpo_demsupport.Rmd
add data/dcpo_replication_input.rda; clean up

claassen_input <- DCPOtools::format_claassen(claassen_input_raw1)
save(claassen_input, file = "data/claassen_input.Rda")
```

>>>>

claassen_input <- DCPOtools::format_claassen(claassen_input_raw1)
save(claassen_input, file = here::here("data", "claassen_input.rda"))

dcpo_replication_input <- DCPOtools::format_dcpo(claassen_input_raw1)
save(dcpo_replication_input, file = here::here("data", "dcpo_replication_input.rda"))
```
